draft 1

### 2016-07-26 finalwriteup/draft.rmd
draft.rmd clash

When comparing Neural Networks to ensemble trees, Ravi Kumar and Ravi [@Kumar2007] found that Neural Networks and ensemble trees were both capable of out-performing the other, depending on the context.

Their study also assessed ensemble techniques, which refers to combinations of two completely different algorithms, and found they can often outperform individual methods. For example, combining the contrasting advantages of Neural Networks and decision trees is a worthwhile ensemble technique. @Tsai2009's study combined these two methods after trialing each one. They were run successively with the Neural Network running first because it had a higher rate of prediction accuracy. Then, to resolve the notorious lack of explanatory qualities, decision trees were employed. The 81% of cases that were correctly predicted by the Neural Network were used to generate decision trees, and in turn decision rules that could be understood by decision makers [@Tsai2009]. This strategy is a promising way to benefit from the strengths of well performing complementary techniques.

>>>>

When comparing Neural Networks to ensemble trees, Ravi Kumar and Ravi [@Kumar2007] found that Neural Networks and ensemble trees were both capable of out-performing the other, depending on the context. For example in financial credit scoring, a study by @Brown2012 found that Random Forests and Boosted Trees consistently outperformed Neural Networks in classification. Logistic regression also outperformed Neural Networks which may align with a theory that most credit scoring datasets are only weakly non-linear [@Brown2012]. This demonstrates how method performance can depend on the dataset and the problem.

@Kumar2007's review also assessed ensemble techniques, which refers to combinations of two completely different algorithms, and found they can often outperform individual methods. For example, combining the contrasting advantages of Neural Networks and decision trees is a worthwhile ensemble technique. @Tsai2009's study combined these two methods after trialing each one. They were run successively with the Neural Network running first because it had a higher predictive accuracy in this case. Then, to resolve the notorious lack of explanatory qualities, decision trees were employed. The 81% of cases that were correctly predicted by the Neural Network were used to generate decision trees, and in turn decision rules that could be understood by decision makers [@Tsai2009]. This strategy is a promising way to benefit from the strengths of well performing complementary techniques.
